Approximating Information-Theoretic Scores\\for Adaptive Tests

### 2021-04-18 paper.tex
Initial Overleaf Import

\documentclass[pmlr,twocolumn,a4paper,10pt]{jmlr}
% \documentclass[pmlr,twocolumn,10pt]{jmlr} % useful when printing your own Letter copy; should not impact layout; do not use for submission
% This class automatically loads the following packages:
% amsmath, amssymb, natbib, graphicx, xcolor, url, algorithm2e, hyperref
  \citestyle{plain} % comment to get author-year; see the natbib docs for more options
\usepackage{isipta2021}
% This style file
% * sets the inputencoding to utf8 (which should be used),
% * loads mathtools (fixes for amsmath) and
% * the font packages textcomp, mathptmx, helvet, and courier (so no font packages should be loaded) and neither should font size be changed
%
%% Choose your variant of English; be consistent
\usepackage[american]{babel}
\usepackage{algorithm,algorithmic,bm}
% \usepackage[british]{babel}
%% Suggested packages, as needed:
% \usepackage{siunitx} % for proper typesetting of numbers and units
\usepackage{booktabs} % commands to create good-looking tables
% \usepackage{rotating} % for sideways figures and tables
% \usepackage{longtable} % for long tables
\usepackage{tikz} % nice language for creating drawings and diagrams
%% Self-defined macros
\newcommand{\swap}[3][-]{#3#1#2} % just an example
%% Frontmatter
% Authors: DO NOT EDIT
\jmlrworkshop{ISIPTA 2021}
\title[Short Title]{% [Short title] can be omitted if title is short enough
  Credal Adaptive Testing
  %Title in Title Case;\titlebreak~ % tilde needed to get space in short title
  %Use the Same Style for Your Section Titles
}

\author{% Authors are listed one per line and grouped per affiliation
  \Name{permutation of Claudio/Giorgia/Francesca/Alessandro}\\ % Accented characters require some attention
  \addr IDSIA
  %\AND
  %\Name{Andrés Cano}\Email{acu@decsai.ugr.es}\\
  %  \Name{Serafín Moral}\Email{smc@decsai.ugr.es}\\
  %\addr Computer Science and Artificial Intelligence, University of Granada, Spain
  %\AND
  %\Name{Jasper {De Bock}}\Email{Jasper.DeBock@UGent.be}\\
  %\addr Electronics and Information Systems, Ghent University, Belgium
}

\begin{document}
\maketitle

\begin{abstract}% No length restrictions, but keep things reasonable
An \emph{adaptive} test is a computer-based testing technique which adjusts the sequence of questions on the basis of the estimated ability level of the test taker. We suggest the use of \emph{credal networks}, a generalization of Bayesian networks based on sets of probability mass functions, to implement adaptive tests exploiting the knowledge of the test developer instead of training on databases of answers. Compared to Bayesian networks, these models might offer higher expressiveness and hence a more reliable modeling of the qualitative expert knowledge. The counterpart is a less straightforward identification of the information-theoretic measure controlling the question-selection and the test-stopping criteria. We elaborate on these issues and propose a sound and computationally feasible procedure. Validation against a Bayesian-network approach on a benchmark about German language proficiency assessments suggests that credal networks can be reliable in assessing the student level and  effective in reducing the number of questions required to do it.
\end{abstract}
\begin{keywords}% Keywords provide context for readers, so put in up to about half a dozen
  keyword, mot clé, Williams-coherence, trefwoord, imprecise Markov chain
\end{keywords}

\section{Single Skill Model}
Let us introduce the discussion by means of a simple example modelling the knowledge level of a student in a particular domain. In order to evaluate such level a number of questions can be asked to the student. We describe the knowledge level (or skill) of the student by means of a single variable $S$. We assume $S$ to be a discrete, ordinal, variable, whose $m$ states $\mathcal{S}:=(s^{(0)},\ldots,s^{(m-1)})$ can be intended as increasing knowledge levels in that domain. Regarding the questions, we initially describe them as Boolean variables, whose true state correspond to a correct answer to the question, while no distinctions between the possible wrong answers are considered.\footnote{Dedicated discussion about abstention.} Let $Q$ with $\mathcal{Q}:=(q,\overline{q})$ denote a generic question we ask to the student. A repository of $n$ questions $\bm{Q}$ is assumed to be available. A \emph{testing} algorithm is a procedure deciding which question and how many questions from $\bm{Q}$ should be asked to the student, on the basis of her previous answers. Algorithm X provides an abstract description of xxx.

\begin{algorithm}[htp!]
    \caption{Given a dataset of student profiles $\bm{S}$\label{alg:simple}}
    \begin{algorithmic}[1]
        \FOR {$s\in\bm{S}$}
        \WHILE{ $h > h^*$}
        \STATE $Q^* \gets \mathrm{FindBestQuestion}(\bm{Q}$)
        \STATE $q^* \gets \mathrm{SimulateAnswer}(\sigma)$
        \STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
        \STATE $h \gets H[P(S|\bm{e}]$
        \ENDWHILE
        \ENDFOR
        \STATE {\bf return} $\arg\max P(s|\bm{e})$
    \end{algorithmic}
\end{algorithm}

\newpage

Let $S$ denote an ordinal variable with $m$ states, denoting the knowledge level of a student with respect to a particular knowledge domain. Let $Q$ denote a question to be

\section{Brainstorming}

@@

\begin{equation}
\sigma_Q := \max_{P\in K} \left[ 
\max \{ P(S=0,Q=0) , P(S=1,Q=0) \}  + \max \{ P(S=0,Q=1),P(S=1,Q=1)\}
\right]
\end{equation}

@@

\begin{algorithm}[htp!]
    \caption{Single skill, credal model\\a dataset of $n$ students $\{s^i\}_{i=1}^n$,\\a dataset of $m$ questions $\mathcal{Q}:=\{Q^j\}_{j=1}^m$,\\
    the credal CPTs of the questions in $\mathcal{Q}$, i.e., $\{\overline{P}(Q^j|S)\}_{j=1}^m$\\
    an upper entropy threshold $\overline{h}^*$,\\
    a score function for questions $\sigma$
    \label{alg:simple}}
    \begin{algorithmic}[1]
    \FOR {$i\gets\{1,\ldots,n\}$}
    \STATE $(\mathcal{Q}',\mathcal{Q}'',\bm{e}) \gets (\mathcal{Q},\emptyset,\emptyset)$
    \WHILE{ $h > h^* \mathrm{\bf and}\, \mathcal{Q}' \neq \mathcal{Q}$}
    \STATE $Q^* \gets \arg\max_{Q \in \mathcal{Q}'}\gamma(Q,\bm{e})$
    \STATE{$\mathcal{Q}'\gets \mathcal{Q}' \setminus \{ Q^*\}$}
    \STATE{$\mathcal{Q}''\gets \mathcal{Q}'' \cup \{ Q^*\}$}
    \STATE{$q^* \gets \mathrm{sampling} \sim P(Q^*|s^i)$}
    \STATE $\mathrm{addChild}(Q,S,P(Q|S))$
    \STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
    \STATE $h \gets H[P(S|\bm{e})]$
    \ENDWHILE
    \STATE $\sigma_i \gets \arg\max_{s\in\mathcal{S}} P(s|\bm{e})$
    \ENDFOR
    \STATE {\bf return} $(\sigma_1,\ldots,\sigma_n)$
    \end{algorithmic}
\end{algorithm}
Three possible scores:
\begin{eqnarray}
    \gamma(Q,\bm{e}) := -H[S|Q,\bm{e}] = -\sum_q P(q) \cdot H[S|\bm{e},q]&&\\
    \gamma'(Q,\bm{e}) :=  -\sum_q P(q) \cdot \max_{s\in\mathcal{S}}  P[s|\bm{e},q]&&\\
    \gamma''(Q,\bm{e}) :=  |P(Q=1|\bm{e})-0.5|&&
\end{eqnarray}

\begin{algorithm}[htp!]
    \caption{Given a dataset of student profiles $\bm{S}$\label{alg:simple}}
    \begin{algorithmic}[1]
        \FOR {$s\in\bm{S}$}
        \WHILE{ $h > h^*$}
        \STATE $Q^* \gets \mathrm{FindBestQuestion}(\bm{Q}$)
        \STATE $q^* \gets \mathrm{SimulateAnswer}(\sigma)$
        \STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
        \STATE $h \gets H[P(S|\bm{e}]$
        \ENDWHILE
        \ENDFOR
        \STATE {\bf return} $\arg\max P(s|\bm{e})$
    \end{algorithmic}
\end{algorithm}

@@

\begin{multline}
\sigma_Q(p,\pi_0,\pi_1)=\\
m\left(\frac{\pi_1 p}{P(q_1)}\right) \cdot P(q_1)  +
m\left(\frac{(1-\pi_1) p}{1-P(q_1)}\right) \cdot (1-P(q_1))\,
\end{multline}

But, as $P(q_1)\geq 0$, then
\begin{multline}
m\left(\frac{\pi_1 p}{P(q_1)}\right) =\\
2max\left(\frac{\pi_1 p}{P(q_1)},1-\frac{\pi_1 p}{P(q_1)} \right) =\\
2max\left(\frac{\pi_1 p}{P(q_1)},\frac{\pi_0(1- p)}{P(q_1)} \right) =\\
\frac{2}{P(q_1)}max\left(\pi_1 p,\pi_0(1- p)\right).\\
\end{multline}

Similarly, as $1-P(q_1)\geq 0$, 
\begin{multline}
m\left(\frac{(1-\pi_1) p}{1-P(q_1)}\right) =\\
\frac{2}{1-P(q_1)}max\left((1-\pi_1) p,(1-\pi_0)(1- p)\right),\\
\end{multline}

@@

However I think we can split the optimization into 4 quadratic optimizations.
Let's use the following parametrization:
\begin{multline}\label{eq:minimization}
\min_{p,\pi_0,\pi_1} \sigma_Q(p,\pi_0,\pi_1) = \\
2\min_{p,\pi_0,\pi_1} \left( \max\{\pi_1 p, \pi_0 (1-p)\} + \\
~~~ \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \right) \approx \\
2\left(\min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\} + \\
~~~ \min_{p,\pi_0,\pi_1} \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \right) 
\end{multline}

Let's consider the first optimization $\min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\}$. It can be written as
$$ \min(\tilde{P}(s=0,q),\tilde{P}(s=1,q)) $$ 
where 
\begin{multline}
\tilde{P}(s=0,q) = \min_{\pi_1 ,p} \pi_1 p \\
\begin{array}{ll}
\text{subject to} & \pi_1 p > \pi_0 (1-p) \\
~&\underline{x} \leq x\leq \overline{x}\\ 
\end{array}
\end{multline}
and 
\begin{multline}
\tilde{P}(s=1,q) = \min_{\pi_0 ,p} \pi_0 (1-p) \\
\begin{array}{ll}
\text{subject to} & \pi_1 p < \pi_0 (1-p)
~&\underline{x} \leq x\leq \overline{x}\\ 
\end{array}
\end{multline}

@@

\paragraph{Adaptive testing.} To add adaptiveness to the above approach, every question should be chosen on the basis of the previous answers. As the goal is to gather information about the student skills, we evaluate the expected \emph{information gain} (IG, i.e., the change in information entropy) associated with each possible new question, and pick the one maximizing this measure. The entropy of a BN over $\bm{X}$ can be computed as $H(\bm{X}):=\sum_{i=1}^n H(X_i|\mathrm{\Pi_{X_i}})$ \cite{koller2009}, where $H(X_i|\mathrm{\Pi_{X_i}}):=\sum_{\pi_{X_i}} H(X_i|\pi_{X_i}) P(\pi_{X_i})$ is the \emph{conditional entropy} for $X$ given its parents and $H(X_i|\pi_{X_i})$ is the entropy of the conditional PMF $P(X_i|\pi_{X_i})$.\footnote{To have entropy levels between zero and one, we define the entropy of the PMF $P(X)$ as $H(X):=-\sum_x P(x) \log_b P(x)$, with $b$ number of states of $X$.} Let $\bm{Y}=\bm{y}$ denote the answers to the questions already asked and $\bm{Y}'$ the set from which the next question should be picked. If the answer to every question $Y'\in\bm{Y}'$ would be known, and denoted by $y'$, the question $\tilde{Y}' \in \bf{\mathbf{Y}'}$ to choose would be the one leading to the largest IG. Yet, as the decision has to be made before the student's answer, conditional entropy should be considered instead, i.e.,
\begin{equation}
\tilde{Y}' := \arg \max_{Y'\in \bm{Y}'} \left[H(\bm{X}|\bm{y})-H(\bm{X}|Y',\bm{y})\right]\,. 
\label{eq:expent}
\end{equation}

\begin{figure*}[htp!]
\centering
\begin{tikzpicture}[auto,scale=.7]
\node[block,node distance=.cm,fill=black!10] (pick) {\begin{varwidth}{1.5cm}\tiny\centering PICK A QUESTION \end{varwidth}};
\node[cloud, left of=pick,node distance=3cm,fill=black!5] (db) {\begin{varwidth}{1.5cm}\tiny\centering QUESTIONS DATABASE\end{varwidth}};
\node[block, right of=pick,node distance=3cm,fill=black!10] (ask) {\begin{varwidth}{1.5cm}\tiny\centering ASK QUESTION\end{varwidth}};
\node[block, right of=ask,node distance=3cm,fill=black!10] (collect) {\begin{varwidth}{1.5cm}\tiny\centering COLLECT ANSWER\end{varwidth}};
\node[decision, below of=collect,node distance=1.4cm] (decide) {\begin{varwidth}{1.5cm}\tiny\centering \textbf{STOPPING RULE? }\end{varwidth}};
\node[block, left of=decide, node distance=3cm,fill=black!10] (stop) {\begin{varwidth}{1.5cm}\tiny\centering END TEST\end{varwidth}};
\node[block, left of=stop, node distance=3cm,fill=black!10] (assign) {\begin{varwidth}{1.5cm}\tiny\centering ASSIGN LEVELS \end{varwidth}};
\path[line] (decide) -- node {\tiny YES}(stop);
\path[line] (decide) -- node[pos=0.1,above] {\tiny NO}(pick);
\path[line,dashed] (db) -- (pick);
\path[line] (pick) -- (ask);
\path[line] (ask) -- (collect);
\path[line] (collect) -- (decide);
\path[line] (decide) -- (stop);
\path[line] (stop) -- (assign);
\end{tikzpicture}
\caption{CAT procedure}
\label{fig:alg}
%\vspace{-1cm}
\end{figure*}

@@

%does not require any, potentially questionable, imputation of the probabilistic ranges provided by the experts.

%Yet, we regard theof BN-AD, we regard the CN approach as more principled and suitable for a direct modeling of qualitative expert knowledge.

%uch a difference disappear if the credal-like variant BN-AD' is considered.
%However, the CN-AD procedure appears to be more effective, as the $u_{65}$ accuracy measure decreases more slowly than the accuracies of BN-AD procedures.  
%Finally,comparing the two BN-AD approaches, one can see that the use of the local instead of the joint entropy does not compromise the effectiveness of the adaptive approach.

%Different decision criteria for the assignment of the skill level, e.g., maximality or e-admissibility, should be considered.
%As a consequence, although BNs achieve better performance when considering the discounted accuracy, CN tests should be preferred whenever the utility is better described by the U65 or U80 measures, that is, whenever being undecided between more level should be preferred than assigning one of them at random. 
%As the true level of the students is unknown, this measure should be regarded as the agreement between to different evaluation strategies. 

@@

%\addplot[color=black!60,mark=star] coordinates { (0.0625,0.94733)(0.125,0.946000)(0.1875,0.943333)(0.25,0.8965000)(0.375,0.744000)(0.5,0.724666)};

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{xcolor} 
\usepackage{amsmath} 
\usepackage{amstext} 
\usepackage{amssymb} 
\usepackage{amsfonts} 
\usepackage{mathptmx} 
\usepackage[scaled=.90]{helvet} 
\usepackage{courier} 
\usepackage{textcomp} 
\usepackage{hyperref} 
\usepackage{array}
\usepackage{varwidth}
\usepackage[american]{babel}
\usepackage{mathtools} % fixes and extends amsmath
\mathtoolsset{mathic}
\allowdisplaybreaks
\usepackage{mathptmx}
\usepackage{tabu}
%\usepackage{breqn}
\usepackage{algorithm,algorithmic,bm}
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
\renewcommand\UrlFont{\color{blue}\rmfamily}
%% Suggested packages, as needed:
\usepackage{booktabs} % commands to create good-looking tables
\usepackage{tikz} % nice language for creating drawings and diagrams - required for 
%drawing custom shapes
\usetikzlibrary{%
	arrows,%
	calc,%
	fit,%
	patterns,%
	plotmarks,%
	shapes.geometric,%
	shapes.misc,%
	shapes.symbols,%
	shapes.arrows,%
	shapes.callouts,%
	% shapes.multipart,%
	% shapes.gates.logic.US,%
	% shapes.gates.logic.IEC,%
	% er,%
	% automata,%
	backgrounds,%
	chains,%
	topaths,%
	trees,%
	petri,%
	mindmap,%
	matrix,%
	% calendar,%
	folding,%
	fadings,%
	through,%
	positioning,%
	scopes,%
	decorations.fractals,%
	decorations.shapes,%
	decorations.text,%
	decorations.pathmorphing,%
	decorations.pathreplacing,%
	decorations.footprints,%
	decorations.markings,%
	shadows}
\usetikzlibrary{arrows,automata,circuits}
\usepackage{pgfplots}
\pgfplotsset{compat=1.13}
\usepackage{pgfkeys}
%\usepackage{trace-pgfkeys}
\begin{document}
\title{Approximating Information-Theoretic Scores\\for Adaptive Tests}
%%\thanks{Supported by organization x.}}
%\titlerunning{Abbreviated paper title}
\author{permutation of Alessandro Antonucci \and
Francesca Mangili \and
Claudio Bonesana\and
Giorgia Adorni}
\authorrunning{F. Author et al.}
\institute{Dalle Molle Institute for Artificial Intelligence USI-SUPSI -- IDSIA \\
\email{\{alessandro,francesca,claudio.bonesana,giorgia.adorni\}@idsia.ch}}
\maketitle          
\begin{abstract}
A test is adaptive when the sequence and the number of questions is tuned on the basis of the estimated skill levels of the test taker. Graphical models such as Bayesian networks allow to model the uncertainty about the questions and the skills in an highly interpretable fashion, especially when coping with multiple skills. Yet, the quantification of the uncertainty in the question/skill relations can be better quantified by interval-valued probabilistic values in the model. This might make inference considerably harded in the underlying model, this being especially the case for the information theoretic quantity generally used for these models. We present.

with xxx. Interval valued quantification

We suggest the use of credal networks, a generalization of Bayesian networks based on sets of probability mass functions, to implement adaptive tests exploiting the knowledge of the test developer instead of training on databases of answers. Compared to Bayesian networks, these models might offer higher expressiveness and hence a more reliable modeling of the qualitative expert knowledge. The counterpart is a less straightforward identification of the 
information-theoretic measure controlling the question-selection and the test-stopping criteria. We elaborate on these issues and propose a sound and computationally feasible procedure. Validation against a Bayesian-network approach 
on a benchmark about German language proficiency assessments suggests that credal networks can be reliable in assessing the student level and  effective in reducing the number of questions required to do it.
%\keywords{credal networks  \and adaptive test \and bayesian network.}
\end{abstract}
\section{Testing Algorithms}
The typical goal of a test or exam is to evaluate the knowledge level of a student or examinee $\sigma$ on the basis of her answers to a number of questions or exercises. Let $\bm{Q}$ denote a repository of questions available to the instructor. The order and the number of questions from $\bm{Q}$ asked to $\sigma$ might not be fixed. We call \emph{testing algorithm} (TA) a procedure taking care of the selection of the sequence of questions asked to the student and able to decide when the test should stop. A standard TA pseudocode is in Algorithm \ref{alg:ta}, where $\bm{e}$ denotes the array of the answers collected from the student $\sigma$.

\begin{algorithm}[htbp!]
    \caption{Testing algorithm. Student profile $\sigma$ and question repository $\bm{Q}$ are inputs.}
    \begin{algorithmic}[1]
    \STATE $\bm{e}=\emptyset$
        \WHILE{ {\bf not} $\tt{Stopping}(\bm{e})$}
        \STATE $Q^* \gets \tt{PickQuestion}(\bm{Q},\bm{e})$
        \STATE $q^* \gets {\tt{Answer}}(Q^*,\sigma)$
        \STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
        \STATE $\bm{Q} \gets \bm{Q} \setminus \{ Q^*\}$
        \ENDWHILE
        \STATE {\bf return} $\tt{Evaluate}(\bm{e})$
    \end{algorithmic}\label{alg:ta}
\end{algorithm}

The Boolean function ${\tt Stopping}$ decides whether or not the test should end, this choice being possibly based on the previous answers as collected in $\bm{e}$. Trivial examples of such stopping rules might be based on the number of questions asked to the student (${\tt Stopping}(\bm{e})=1$ if and only if $|\bm{e}|>n$) or on the number of correct answers provided that a maximum number of questions is not exceeded. Function ${\tt PickQuestion}$ is instead in charge of deciding which question should be asked to the student from the repository $\bm{Q}$. A TA is called \emph{adaptive} when this function is based on the previous answers $\bm{e}$. Trivial non-adaptive strategies might consist in randomly picking an element of $\bm{Q}$ or following a fixed order. Function ${\tt Answer}$ is simply collecting (or simulating) the answer of the student $\sigma$ to a particular question $Q$. In our assumptions, this answer is not affected by the previous answers to other questions.\footnote{Generalized setups where the quality of the student answer is affected by the previous answers will be discussed at the end of the paper. This might include a \emph{fatigue} model negatively affecting the quality of the answers when many questions have been already answered as well as the presence of \emph{revealing} questions that might improve the quality of other answers.}

Finally, the ${\tt Evaluate}$ function decides the overall judgement for the test (e.g., a numerical grade or a pass/fail Boolean) on the basis of all the answers collected after the test termination. Trivial examples of such function are the percentage of correct answers or a Boolean that is true when a sufficient percentage of correct answers has been provided. Note also that in our assumptions the TA is \emph{exchangeable}, i.e., the stopping rule, the question finder and the evaluation function are invariant with respect to permutations of $\bm{e}$. In other words, the would pick the same next question and the same evaluation for two students who provided the same list of answers in two different orders and similarly would decide to stop or not to stop in the same way.

The typical goal of a TA is to achieve a reliable evaluation of the student $\sigma$. As each answer is assumed to improve such quality, asking all the questions, no matter their order because of the exchangeability assumption, would be an obvious choice. Yet, asking all the questions in the repository might be impractical (e.g., because of time limitations) in some cases or just provide an unnecessary burden to the students. The goal of a good TA is therefore to trade off the accuracy of the evaluation and the number of questions.\footnote{In some generalized setups, other elements such as the \emph{serendipity} to avoid boring sequences of questions might be also considered.}

Item response theory is a popular *** Something about IRT here ***. Most of these approaches are based an a unidimensional representation of the student knowledge level. Proposals to cope with multidimensional IRTs have been considered, but this results critical when coping with dependencies between them. For this reason probabilistic modelling can be considered. This is the topic of the next section.

\section{Bayesian Adaptive Testing Algorithms}
In the setup of algorithm.

Let us introduce the discussion by means of a simple example modelling the knowledge level of a student in a particular domain. In order to evaluate such level a number of questions can be asked to the student. We describe the knowledge level (or skill) of the student by means of a single variable $S$. We assume $S$ to be a discrete, ordinal, variable, whose $m$ states $\mathcal{S}:=(s^{(0)},\ldots,s^{(m-1)})$ can be intended as increasing knowledge levels in that domain. Regarding the questions, we initially describe them as Boolean variables, whose true state correspond to a correct answer to the question, while no distinctions between the possible wrong answers are considered.\footnote{Dedicated discussion about abstention.} Let $Q$ with $\mathcal{Q}:=(q,\overline{q})$ denote a generic question we ask to the student. A repository of $n$ questions $\bm{Q}$ is assumed to be available. A \emph{testing} algorithm is a procedure deciding which question and how many questions from $\bm{Q}$ should be asked to the student, on the basis of her previous answers. Algorithm X provides an abstract description of xxx.

	%
	%
	\section{Brainstorming}

@@

	\begin{equation}
		\sigma_Q := \max_{P\in K} \bigl[ 
		\max \{ P(S=0,Q=0) , P(S=1,Q=0) \}  + \max \{ P(S=0,Q=1),P(S=1,Q=1)\}
		\bigr]
	\end{equation}

@@

	\begin{algorithm}[htp!]
		\caption{Single skill, credal model\\a dataset of $n$ students $\{s^i\}_{i=1}^n$,\\a 
		dataset of $m$ questions $\mathcal{Q}:=\{Q^j\}_{j=1}^m$,\\
			the credal CPTs of the questions in $\mathcal{Q}$, i.e., 
			$\{\overline{P}(Q^j|S)\}_{j=1}^m$\\
			an upper entropy threshold $\overline{h}^*$,\\
			a score function for questions $\sigma$
			\label{alg:simple2}}
		\begin{algorithmic}[1]
			\FOR {$i\gets\{1,\ldots,n\}$}
			\STATE $(\mathcal{Q}',\mathcal{Q}'',\bm{e}) \gets 
			(\mathcal{Q},\emptyset,\emptyset)$
			\WHILE{ $h > h^* \mathrm{\bf and}\, \mathcal{Q}' \neq \mathcal{Q}$}
			\STATE $Q^* \gets \arg\max_{Q \in \mathcal{Q}'}\gamma(Q,\bm{e})$
			\STATE{$\mathcal{Q}'\gets \mathcal{Q}' \setminus \{ Q^*\}$}
			\STATE{$\mathcal{Q}''\gets \mathcal{Q}'' \cup \{ Q^*\}$}
			\STATE{$q^* \gets \mathrm{sampling} \sim P(Q^*|s^i)$}
			\STATE $\mathrm{addChild}(Q,S,P(Q|S))$
			\STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
			\STATE $h \gets H[P(S|\bm{e})]$
			\ENDWHILE
			\STATE $\sigma_i \gets \arg\max_{s\in\mathcal{S}} P(s|\bm{e})$
			\ENDFOR
			\STATE {\bf return} $(\sigma_1,\ldots,\sigma_n)$
		\end{algorithmic}
	\end{algorithm}
	Three possible scores:
	\begin{eqnarray}
		\gamma(Q,\bm{e}) := -H[S|Q,\bm{e}] = -\sum_q P(q) \cdot H[S|\bm{e},q]&&\\
		\gamma'(Q,\bm{e}) :=  -\sum_q P(q) \cdot \max_{s\in\mathcal{S}}  P[s|\bm{e},q]&&\\
		\gamma''(Q,\bm{e}) :=  |P(Q=1|\bm{e})-0.5|&&
	\end{eqnarray}

	\begin{algorithm}[htp!]
		\caption{Given a dataset of student profiles $\bm{S}$\label{alg:simple3}}
		\begin{algorithmic}[1]
			\FOR {$s\in\bm{S}$}
			\WHILE{ $h > h^*$}
			\STATE $Q^* \gets \mathrm{FindBestQuestion}(\bm{Q}$)
			\STATE $q^* \gets \mathrm{SimulateAnswer}(\sigma)$
			\STATE $\bm{e} \gets \bm{e} \cup \{ Q^*=q^* \}$
			\STATE $h \gets H[P(S|\bm{e}]$
			\ENDWHILE
			\ENDFOR
			\STATE {\bf return} $\arg\max P(s|\bm{e})$
		\end{algorithmic}
	\end{algorithm}

@@

	\begin{multline}
		\sigma_Q(p,\pi_0,\pi_1)=\\
		m\bigl(\frac{\pi_1 p}{P(q_1)}\bigr) \cdot P(q_1)  +
		m\bigl(\frac{(1-\pi_1) p}{1-P(q_1)}\bigr) \cdot (1-P(q_1))\,
	\end{multline}

	But, as $P(q_1)\geq 0$, then
	\begin{multline}
		m\bigl(\frac{\pi_1 p}{P(q_1)}\bigr) =\\
		2max\bigl(\frac{\pi_1 p}{P(q_1)},1-\frac{\pi_1 p}{P(q_1)} \bigr) =\\
		2max\bigl(\frac{\pi_1 p}{P(q_1)},\frac{\pi_0(1- p)}{P(q_1)} \bigr) =\\
		\frac{2}{P(q_1)}max\bigl(\pi_1 p,\pi_0(1- p)\bigr).\\
	\end{multline}

	Similarly, as $1-P(q_1)\geq 0$, 
	\begin{multline}
		m\bigl(\frac{(1-\pi_1) p}{1-P(q_1)}\bigr) =\\
		\frac{2}{1-P(q_1)}max\bigl((1-\pi_1) p,(1-\pi_0)(1- p)\bigr),\\
	\end{multline}

@@

	However I think we can split the optimization into 4 quadratic optimizations.
	Let's use the following parametrization:
	\begin{multline}\label{eq:minimization}
		\min_{p,\pi_0,\pi_1} \sigma_Q(p,\pi_0,\pi_1) = \\
		2\min_{p,\pi_0,\pi_1} \bigl( \max\{\pi_1 p, \pi_0 (1-p)\} + \\
		~~~ \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \bigr) \approx \\
		2 \bigl( \min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\} + \\
		~~~ \min_{p,\pi_0,\pi_1} \max\{(1-\pi_1 )p, (1-\pi_0) (1-p)\} \bigr) 
	\end{multline}

	Let's consider the first optimization $\min_{p,\pi_0,\pi_1}  \max\{\pi_1 p, \pi_0 (1-p)\}$. It 
	can be written as
	$$ \min(\tilde{P}(s=0,q),\tilde{P}(s=1,q)) $$ 
	where

	\begin{multline}
		\tilde{P}(s=0,q) = \min_{\pi_1 ,p} \pi_1 p \\
		\begin{array}{ll}
			\text{subject to} & \pi_1 p > \pi_0 (1-p) \\
			~&\underline{x} \leq x\leq \overline{x}\\ 
		\end{array}
	\end{multline}
	and 
	\begin{multline}
		\tilde{P}(s=1,q) = \min_{\pi_0 ,p} \pi_0 (1-p) \\
		\begin{array}{ll}
			\text{subject to} & \pi_1 p < \pi_0 (1-p)\\
			~&\underline{x} \leq x\leq \overline{x}\\ 
		\end{array}
	\end{multline}

@@

	\paragraph{Adaptive testing.} To add adaptiveness to the above approach, every 
	question should be chosen on the basis of the previous answers. As the goal is to 
	gather information about the student skills, we evaluate the expected 
	\emph{information gain} (IG, i.e., the change in information entropy) associated with 
	each possible new question, and pick the one maximizing this measure. The entropy of 
	a BN over $\bm{X}$ can be computed as $H(\bm{X}):=\sum_{i=1}^n 
	H(X_i|\mathrm{\Pi_{X_i}})$ \cite{koller2009}, where 
	$H(X_i|\mathrm{\Pi_{X_i}}):=\sum_{\pi_{X_i}} H(X_i|\pi_{X_i}) P(\pi_{X_i})$ is the 
	\emph{conditional entropy} for $X$ given its parents and $H(X_i|\pi_{X_i})$ is the 
	entropy of the conditional PMF $P(X_i|\pi_{X_i})$.\footnote{To have entropy levels 
	between zero and one, we define the entropy of the PMF $P(X)$ as $H(X):=-\sum_x 
	P(x) \log_b P(x)$, with $b$ number of states of $X$.} Let $\bm{Y}=\bm{y}$ denote the 
	answers to the questions already asked and $\bm{Y}'$ the set from which the next 
	question should be picked. If the answer to every question $Y'\in\bm{Y}'$ would be 
	known, and denoted by $y'$, the question $\tilde{Y}' \in \bf{\mathbf{Y}'}$ to choose 
	would be the one leading to the largest IG. Yet, as the decision has to be made before 
	the student's answer, conditional entropy should be considered instead, i.e.,
	\begin{equation}
		\tilde{Y}' := \arg \max_{Y'\in \bm{Y}'} 
		\bigl[H(\bm{X}|\bm{y})-H(\bm{X}|Y',\bm{y})\bigr]\,. 
		\label{eq:expent}
	\end{equation}

	\begin{figure*}[htp!]
		\centering
		\begin{tikzpicture}[auto,scale=.7]
			\node[node distance=.cm,fill=black!10] (pick) 
			{\begin{varwidth}{1.5cm}\tiny\centering PICK A QUESTION \end{varwidth}};
			\node[cloud, left of=pick,node distance=3cm,fill=black!5] (db) 
			{\begin{varwidth}{1.5cm}\tiny\centering QUESTIONS DATABASE\end{varwidth}};
			\node[right of=pick,node distance=3cm,fill=black!10] (ask) 
			{\begin{varwidth}{1.5cm}\tiny\centering ASK QUESTION\end{varwidth}};
			\node[right of=ask,node distance=3cm,fill=black!10] (collect) 
			{\begin{varwidth}{1.5cm}\tiny\centering COLLECT ANSWER\end{varwidth}};
			\node[below of=collect,node distance=1.4cm] (decide) 
			{\begin{varwidth}{1.5cm}\tiny\centering \textbf{STOPPING RULE? 
			}\end{varwidth}};
			\node[ left of=decide, node distance=3cm,fill=black!10] (stop) 
			{\begin{varwidth}{1.5cm}\tiny\centering END TEST\end{varwidth}};
			\node[left of=stop, node distance=3cm,fill=black!10] (assign) 
			{\begin{varwidth}{1.5cm}\tiny\centering ASSIGN LEVELS \end{varwidth}};
			\draw[] (decide) -- node {\tiny YES}(stop);
			\draw[] (decide) -- node[pos=0.1,above] {\tiny NO}(pick);
			\draw[dashed] (db) -- (pick);
			\draw[] (pick) -- (ask);
			\draw[] (ask) -- (collect);
			\draw[] (collect) -- (decide);
			\draw[] (decide) -- (stop);
			\draw[] (stop) -- (assign);
		\end{tikzpicture}
		\caption{CAT procedure}
		\label{fig:alg}
		%\vspace{-1cm}
	\end{figure*}

@@

	%does not require any, potentially questionable, imputation of the probabilistic ranges 
	%provided by the experts.

	%Yet, we regard theof BN-AD, we regard the CN approach as more principled and 
	%suitable for a direct modeling of qualitative expert knowledge.

	%uch a difference disappear if the credal-like variant BN-AD' is considered.
	%However, the CN-AD procedure appears to be more effective, as the $u_{65}$ 
	%accuracy measure decreases more slowly than the accuracies of BN-AD procedures.  
	%Finally,comparing the two BN-AD approaches, one can see that the use of the local 
	%instead of the joint entropy does not compromise the effectiveness of the adaptive 
	%approach.

	%Different decision criteria for the assignment of the skill level, e.g., maximality or 
	%e-admissibility, should be considered.
	%As a consequence, although BNs achieve better performance when considering the 
	%discounted accuracy, CN tests should be preferred whenever the utility is better 
	%described by the U65 or U80 measures, that is, whenever being undecided between 
	%more level should be preferred than assigning one of them at random. 
	%As the true level of the students is unknown, this measure should be regarded as the 
	%agreement between to different evaluation strategies. 

@@

	%\addplot[color=black!60,mark=star] coordinates { 
	%(0.0625,0.94733)(0.125,0.946000)(0.1875,0.943333)(0.25,0.8965000)(0.375,0.744000)(0.5,0.724666)};
